The Effect of a Second AIDS Defining Illness on Survival in the MACS

### 2015-05-05 paper.Rmd
Add commented out code for matching

```{r matching, eval=FALSE}
library(MatchIt)
```

>>>>

```{r matching, eval=FALSE}
library(MatchIt)
# ########################################################################
# ## Q9c Match on propensity score and compare the propensity score 
# ##	distribution overlap between HIV/HAART and HIV-uninfected before
# ##	and after matching.
# ########################################################################
# 
# ## We will use the package "MatchIt" to perform matches
# ##	note: you can have the function matchit actually calculate the propensity score
# ##		but as we've already calculated cpoe we can have matchit use our already 
# ##		defined propensity score by the option "distance=dat$cpoe" located in the code below
# ##	note: we chose a caliper of 0.07, by iteratively going through a search between 0 and .5
# ##		at a 0.01 step and chose the caliper that maximized the percent balance improvement
# ##		for distance (e.g. propensity score), age, and bmi.
# 
# set.seed(8771)
# match.set <- matchit(hivhrt~age + bmi,data=dat,distance=dat$cpoe,method="nearest",caliper=.07,discard="both")
# 
# ## let's check out the diagnostics
# 
# ## numerical check
# print(sum.match <- summary(match.set,standardize=T))
# 
# ## graphical check
# plot(match.set,type="jitter",interactive=F)
# plot(match.set,type="hist")
# plot(sum.match,interactive=F)
# 
# matched.dat <- match.data(match.set,"all")
# 
# ## how many individuals in matched.dat?
# nrow(matched.dat)
# 
# ## How many events do we have in the matched data?
# sum(matched.dat$dm)
# 
# ########################################################################
# ## Q10a Get HRs after matching
# ########################################################################
# 
# ph.match <- coxph(Surv(time=t,event=dm)~hivhrt,
# 				data=matched.dat,method="efron")
# summary(ph.match)
# 
# 
# 
# ########################################################################
# ## Q10b Get HRs after matching with higher caliper
# ########################################################################
# 
# 
# set.seed(1428)
# match2.set <- matchit(hivhrt~age + bmi,data=dat,distance=dat$cpoe,method="nearest",caliper=.5,discard="both")
# 
# ## let's check out the diagnostics
# 
# ## numerical check
# print(sum.match2 <- summary(match2.set,standardize=T))
# 
# ## graphical check
# plot(match2.set,type="jitter",interactive=F)
# plot(sum.match2,interactive=F)
# 
# matched2.dat <- match.data(match2.set,"all")
# 
# ## how many individuals in matched.dat?
# nrow(matched2.dat)
# 
# ##
# sum(matched2.dat$dm)
# 
# ph.match2 <- coxph(Surv(time=t,event=dm)~hivhrt,data=matched2.dat,method="efron")
# summary(ph.match2)
# 
# 
# 
# 
# ########################################################################
# ## Q10c Get HRs after subclassification
# ########################################################################
# 
# 
# dat$hivhrtn <- as.numeric(dat$hivhrt)-1
# sub.set <- matchit(hivhrtn~age + bmi,data=dat,method="subclass",sub.by="all",subclass=5,discard="both")
# 
# summary(sub.set,standardize=T)
# plot(sub.set,type="jitter",interactive=F)
# plot(summary(sub.set,standardize=T),interactive=F)
# 
# sub.dat <- match.data(sub.set,"all")
# ph.sub <- coxph(Surv(time=t,event=dm)~hivhrtn+strata(subclass),data=sub.dat,method="efron")
# summary(ph.sub)
```
